Growing libraries of concepts with wake-sleep program induction

### 2018-07-23 talk.tex
More figures, slides for the talk
figure changes

\begin{frame}[t]{DSL learning as Bayesian inference}
  \includegraphics[width = 11cm]{figures/animation/EC.eps}

@@

  \vfill
  Gray: Observed.\\
  White: Latent.\\
  Boxed (plate): Repeated.\\

\end{frame}
\begin{frame}[t]{DSL learning as \alert{amortized} Bayesian inference}
  \includegraphics[width = 11cm]{figures/animation/DC.eps}

  \vfill
  Recognition model: Neural net.\\
  Red: Bottom-up inference.\\
  Gray: Observed.\\
  White: Latent.\\
  Boxed (plate): Repeated.\\

@@

>>>>

\begin{frame}[t]{DSL learning as Bayesian inference}
  %  \includegraphics[width = 11cm]{figures/animation/EC.eps}
\centering  \begin{tikzpicture}[scale=1.3,line width=0.5mm]

  \node[latent,scale=1] at (3.5,3) (dx){DSL};
  \node[latent,scale=1] at ([yshift=-1.5cm]dx) (zp){prog};
  \node[obs,scale=1] at ([yshift=-2cm]zp) (xp) {data};
  \node[latent,scale=1] at ([xshift=2cm]zp) (zp1){prog};
  \node[obs,scale=1] at ([xshift=2cm]xp) (xp1) {data};
  \draw [->] (zp1.south) -- (xp1.north);
  \draw [->] (dx.south) -- (zp1.north);
  %\draw [->,red] (xp1.east) to[out = 30,in = -30] node(nn){} (zp1.east);
%  \node at (nn) {\NeuralNetwork{0.5}};

  \node[latent,scale=1] at ([xshift=-2cm]zp) (zp1){prog};
  \node[obs,scale=1] at ([xshift=-2cm]xp) (xp1) {data};
  \draw [->] (zp1.south) -- (xp1.north);
  \draw [->] (dx.south) -- (zp1.north);
%  \draw [->,red] (xp1.east) to[out = 30,in = -30] node(nn){} (zp1.east);
%  \node at (nn) {\NeuralNetwork{0.5}};

%  \draw [->,red] (xp.east) to[out = 30,in = -30] node(nn){} (zp.east);
 % \node at (nn) {\NeuralNetwork{0.5}};
  \draw [->] (dx.south) -- (zp.north);
  \draw [->] (zp.south) -- (xp.north);

  %\node[shift={+(0,-1.7)}] at (nn) { $Q$  };

  \end{tikzpicture}

@@

  %% \vfill
  %% Gray: Observed.\\
  %% White: Latent.\\
  %% Boxed (plate): Repeated.\\

\end{frame}
\newcommand{\NeuralNetwork}[1]{    \begin{tikzpicture}[x=2.5cm,y=1.25cm,transform canvas={scale=#1,shift={+(-1,2.5)}}]
      \tikzstyle{neuron}=[circle,fill=blue!50,minimum size=20pt]
      \fill[fill=white] (-0.25,-0.5) rectangle (2.25,-4.5);
      \node[rectangle] at (1,1) {};
      \foreach \name / \y in {1,...,4}
          \node[neuron] (I-\name) at (0,-\y) {};
      \foreach \name / \y in {1,...,3}
          \node[neuron] (H-\name) at (1,-\y-0.5) {};
      \foreach \name / \y in {1,...,4}
          \node[neuron] (O-\name) at (2,-\y) {};
      \foreach \source in {1,...,4}
          \foreach \dest in {1,...,3}
              \draw [-latex] (I-\source) -- (H-\dest);
      \foreach \source in {1,...,3}
          \foreach \dest in {1,...,4}
              \draw [-latex] (H-\source) -- (O-\dest);
    \end{tikzpicture}}
\begin{frame}[t]{DSL learning as \alert{amortized} Bayesian inference}
\centering  \begin{tikzpicture}[scale=1.3,line width=0.5mm]

  \node[latent,scale=1] at (3.5,3) (dx){DSL};
  \node[latent,scale=1] at ([yshift=-1.5cm]dx) (zp){prog};
  \node[obs,scale=1] at ([yshift=-2cm]zp) (xp) {data};
  \node[latent,scale=1] at ([xshift=2cm]zp) (zp1){prog};
  \node[obs,scale=1] at ([xshift=2cm]xp) (xp1) {data};
  \draw [->] (zp1.south) -- (xp1.north);
  \draw [->] (dx.south) -- (zp1.north);
  \draw [->,red] (xp1.east) to[out = 30,in = -30] node(nn){} (zp1.east);
%  \node at (nn) {\NeuralNetwork{0.5}};

  \node[latent,scale=1] at ([xshift=-2cm]zp) (zp1){prog};
  \node[obs,scale=1] at ([xshift=-2cm]xp) (xp1) {data};
  \draw [->] (zp1.south) -- (xp1.north);
  \draw [->] (dx.south) -- (zp1.north);
  \draw [->,red] (xp1.east) to[out = 30,in = -30] node(nn){} (zp1.east);
%  \node at (nn) {\NeuralNetwork{0.5}};

  \draw [->,red] (xp.east) to[out = 30,in = -30] node(nn){} (zp.east);
  \node at (nn) {\NeuralNetwork{0.25}};
  \draw [->] (dx.south) -- (zp.north);
  \draw [->] (zp.south) -- (xp.north);

  %\node[shift={+(0,-1.7)}] at (nn) { $Q$  };

  \end{tikzpicture}

@@

\begin{frame}{Turtle graphics --- Some results}
  \centering
  \includegraphics[width=9cm]{figures/dreams/montageTalk.eps}
\end{frame}
